Syntax Is All You Need: A Universal-Language Approach to Mutant Generation

### 2023-06-01 paper/ICSEfixnotes.tex
more detail

2.  we genuinely should take the time to improve the equivalence estimates, and try to do PIT

@@

>>>>

2.  we genuinely should take the time to improve the equivalence estimates, and try to do PIT (my proposal:  do up to 30 unkilled mutants, and look at PIT source reports to try to figure equivalency there)

@@

4. change way we cite the ICSE 2018 tool paper; redact the details and flat say we had an early tool paper on the regexp idea with little data but it's ours, we are the same tool
